---
title: "Deliverables and Guidelines for Future Use"
author: "Scott McCain"
date: "May 26, 2017"
output:
  html_document: default
  pdf_document: default
---

### Index

1) [Summary of Deliverables](#summary-of-deliverables)
2) [Framework for Fixed Station Websites](#framework-for-fixed-station-websites)
    + [Example of Initializing and Populating a New Folder System](#example-of-initializing-and-populating-a-new-folder-system)
3) [R Scripts for Fixed Station Website Populating](#r-scripts-for-fixed-station-website-populating)
    + [Key Considerations for Future Use](#key-considerations-for-future-use)
    + [Function Descriptions](#function-descriptions)

### Summary of Deliverables

-	Wrote a flexible series of R scripts to perform various objectives: file conversion, file transfer, and plotting. This framework (detailed below) can be used for any other fixed station websites.
-	Updated the Bedford Basin Monitoring Program, by completing plots from 1999-2009, and ODFs from 1999-2009.
-	Converted all current ODFs to CSVs onto the website, and created a continually updating aggregated CSV with consistent formatting.
-	Worked with Patrick Upson to update the look and feel of the website.
-	Contributed all code and development through the collaborative and version-controlled system Git and GitHub.
-	Met with stakeholders to establish goals and use-cases for website
    +	Catherine Johnson, Emmanuel Devred, Dave Brickman, Dave Herbert, Andrew Cogswell (BIO)
    +	Dave Covey and Richard Davis (Dalhousie, MEOPAR)

### Framework for Fixed Station Websites

1)	Populating an FTP:
    +	Declare working directories, determine file naming structure.
    +	Create folders in FTP with similar structure to BBMP FTP (this can be done automatically with `directory_structure()`).
    +	Using the transfer, conversion, and plotting functions, fill in the folders.
    +	Using the bulk data aggregation script, create aggregated csv of station.
2) Create a site-context map:
    +	Adjust the latitude and longitude limits for the map R script, and produce a corresponding site map (easily adapted from `Bedford_Basin_Map.R`)
3)	Write detailed site description and sampling overview:
    +	Similar to the current text on the BBMP website, a detailed overview of sampling should be written (and translated). This text should overview why this site was chosen, what sampling is done, and any other important site characteristics. 
    
#### Example of Initializing and Populating a New Folder System

This simple example demonstrates how to create and populate a new folder system:

<style>
div.blue pre { background-color:lightblue1; }
div.blue pre.r { background-color:lightcyan; }
</style>

<div class = "blue">
```{r initial, echo = TRUE, warning = FALSE, message = FALSE, eval = FALSE}
ftp_name <- "HL2"

# Creates file directory structure
directory_structure(parent_directory = ftp_name, first_year = 1999)

#populate the folders
for(i in 1999:2017){
  #Completes all profile image archives.
  odf_year_plots(year = i, 
                 out_root = paste("~/", ftp_name, "/Profile_Image_Archives/", sep = ""), 
                 site_code = "666")
  # Completes all CSV archives.
  transfer_files_csv(year = i, 
                     out_root = paste("~/", ftp_name, "/CSV/", sep = ""), 
                     site_code = "666")
  # Completes all ODF archives.
  transfer_files_odf(year = i, 
                     out_root = paste("~/", ftp_name, "/ODF/", sep = ""), 
                     site_code = "666")
}

#Use bulk_data_aggregation.R if a single data file is required - set the arguments (e.g. year range) within.

#That's it! This will be written to your home directory (e.g. Documents), but can be then manually copied to a new FTP.
```
</div>

### R Scripts for Fixed Station Website Populating

```{r setup, echo = FALSE, warning = FALSE, message = FALSE, include = FALSE}
knitr::opts_chunk$set(cache=FALSE)
source("~/MoPS/odf_plot_functions.R")
source("~/MoPS/odf_file_finder_lister.R")
source("~/MoPS/transfer_functions_ODF_and_CSV.R")
source("~/MoPS/FTP_folder_initialization.R")
```

The following functions can be used to: 

  1) Populate a designated File Transfer Protocol (FTP) with backlogged profile images, ODF cast files, and CSVs, and corresponding summary (.tsv) files.
  2) Create an aggregated .csv file of all casts, with date labels.

These functions are a general framework for doing the objectives above, however have been specifically applied to the Bedford Basin Monitoring Program. Therefore, the default arguments are for the BBMP. Below, I describe the functions, their use, and how to adopt them for future use.

&nbsp;&nbsp;General Use

* `odf_file_lister()`: Produces a set of odf files that are matched for certain naming conventions. e.g. searches for only Bedford Basin 667.  
* `directory_lister_wrapper()`: A wrapper function for the `odf_file_lister()`, which switches to the Src if files aren't present.  
* `directory_structure()`: Creates a directory structure with three layers: (1) the FTP name (e.g. BBMP), (2) all sub-directories for file types (e.g. CSV, ODF, and Profile_Image_Archives), and (3) sub-folders for every year within a set year range. 

&nbsp;&nbsp;Plotting Functions

* `fluorescence_oxygen_plot()`: Creates a the last fluorescence/oxygen plot in the four-panels of plots. Function needed for years that have one or both variables missing.  
* `odf_plot_function()`: Creates the four panel plot.  
* `odf_year_plots()`: Creates the four panel plot for an year.  

&nbsp;&nbsp;File Transfer and Conversion   

* `odf_date_finder()`: Simple function that returns the date of an ODF.
* `odf_file_renamer()`: Reads in an ODF file, and depending if it was read from the Arc (double quality controlled), or from the Src, the name will be reformated.  
* `transfer_files_odf()`: Files are renamed and copied from the Arc or Src and transferred into the BBMP site FTP.  
* `transfer_files_csv()`: Files are renamed and converted from the Arc or Src and transferred into the BBMP site FTP.

#### Key Considerations for Future Use

There are two expected problems with adapting this code for another fixed station.

1) Working directory switching.
2) File naming and searching.

To address these:

1) Use the arguments `arc_root` and `src_root` (described in functions below) to determine the first location to look and the second location to look for source files, respectively. Use the argument `out_root` to set the location for files to be copied/written to.
2) Adapt the function `odf_file_lister()` to search for a specific file naming pattern.

****

#### Function Descriptions
****
`odf_file_lister()` lists all files in a working directory from some pattern (e.g. searching for the site code "667"). These patterns differ if the file was found in the Src or the Arc. This function would need to be altered to accomodate a new file naming convention.

<div class = "blue">
```{r file_lister, echo = TRUE, tidy = FALSE, message = FALSE, comment = NA, keep.source = TRUE}
odf_file_lister
```
</div>
****
`directory_lister_wrapper()` is the function that would enable new directory switching. The arguments `arc_root` and `src_root` are critical for this. An important aspect of this function is that global variables are declared depending on where the files are located (via `use_src <<- TRUE/FALSE`). This allows the functions to "talk" to each other, which is particularly important for naming.  

If the naming conventions are the same as the BBMP, then a first try would simply be to switch the directory locations in this function (the default is set for the BBMP).

<div class = "blue">
```{r directory_lister_wrapper, echo = TRUE, tidy = TRUE, comment = NA}
directory_lister_wrapper
```
</div>
****
`directory_structure()` creates a system of directories and sub-directories for subsequently populating with ODFs, CSVs, and profile images. If another file type is added (e.g. NetCDF), this could be adapted easily with the argument `sub_directories = c("CSV", "ODF", "Profile_Image_Archives", "NetCDF")`.

<div class = "blue">
```{r direc_struc, echo = TRUE, tidy = FALSE, message = FALSE, comment = NA}
directory_structure
```
</div>
****
`fluorescence_oxygen_plot` is a function for handling the fluorescence/oxygen plot in the four-panel plot. It is most useful for earlier years (~2000) in which only one, or neither, of these variables were measured.

<div class = "blue">
```{r flu_plot, echo = TRUE, tidy = FALSE, message = FALSE, comment = NA}
fluorescence_oxygen_plot
```
</div>
****
`odf_plot_function()` is the core function for creating plots from a single ODF file. Note that there is no default for the `out_root` argument, as it is inherited from the wrapper function `odf_year_plots()`.

<div class = "blue">
```{r plot_root, echo = TRUE, tidy = FALSE, message = FALSE, comment = NA}
odf_plot_function
```
</div>
****
`odf_year_plots()` is a wrapper function to make a plot for every ODF in a given year.

<div class = "blue">
```{r plot_wrapper, echo = TRUE, tidy = FALSE, message = FALSE, comment = NA}
odf_year_plots
```
</div>

****
`odf_file_renamer()` renames files dynamically dependent on the original file location (src vs. arc). (Note this is recently deprecated, file names now reflect where they were found.)

<div class = "blue">
```{r odf_file_renam, echo = TRUE, tidy = FALSE, message = FALSE, comment = NA}
odf_file_renamer
```
</div>
****
`transfer_files_csv()` and `transfer_files_odf()` are very similar functions, in that they both transfer files. The key difference is that ODF files can simply be copied, while csv files have to be opened and rewritten into a different directory.

<div class = "blue">
```{r transferring_files, echo = TRUE, tidy = FALSE, message = FALSE, comment = NA}
transfer_files_csv
transfer_files_odf
```
</div>